An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-17 poly-embed-journal/poly-embed-journal.tex
meeting edits

\begin{proposition}\label{prop:embed-bayes-risks}
  Let discrete loss $\ell$ be given.
  Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % Let discrete loss $\ell:\R\to\reals^Y$ be given.
  % Then $L:\reals^d\to\reals^\Y$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{4/2/2021 first part of the proof should be done now.}
  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$; take $\U := \varphi(\Sc)$.
  Since $\Sc$ is representative for $\ell$, by embedding condition (ii) we have $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$, so $\U$ is representative for $L$.
  % for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
  % In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, 
  By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$ and $\risk{L} = \risk{L|_{\U}}$.
  % \raft{Commented out: the symmetric argument that representation goes both ways under an embedding.  I'm thinking we should expand on this perspective in section 5, maybe introduce a notion of equivalence between any two losses (discrete or otherwise), and define trim in that context.}
  % Taking $\U := \varphi(\Sc)$, we have that $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), for all $p\in\simplex$ we have
  \begin{equation*}
    \risk{\ell}(p) = \risk{\ell|_\Sc}(p) = \min_{r \in \Sc}\inprod{p}{\ell(r)} = \min_{r \in \Sc}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~.
  \end{equation*}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell:\R \to \reals^\Y_+$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\cite[Corollary 13.3.1]{rockafellar1997convex}.
  Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.
  Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
  As $C$ is polyhedral, so is $L$.
  We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Minimum Representative Sets and Non-redundancy}
\label{sec:min-rep-sets}

% commented out 19 Apr 21
% \raf{Some thoughts on this section:
% \begin{itemize}
% \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
% \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
%   \begin{itemize}
%   \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
%   \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
%   \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
%   \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
%   \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
%   \end{itemize}
% \end{itemize}}
% \jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
% There are a few results that are well-explained by this:
% \begin{itemize}
%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimum representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
% \end{itemize}
% This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

@@

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
  Let $\U$ be a finite representative set for $L$ eliciting $\Gamma$.
  $\U$ is a minimum representative set for $L$ if and only if $L|_{\U}$ is non-redundant.
\end{proposition}
\begin{proof}
  $\Rightarrow$  
  We show the contrapositive: suppose $L|_{\U}$ is redundant.
  Then there is a $r,r' \in \U$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
  Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
  Therefore, $\U \setminus \{r\}$ still a representative set, so $\U$ is not minimum.

@@

%Set up notation and define $g,G$
Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
\begin{claim}
	We may write $f(p) = \min_{v\in\V} \inprod{p}{v}$ for some finite set $\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
\end{claim}
\begin{proof}
  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
  \raf{Make formal}
  For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
  If $p \not \in \simplex$, then $f(p) = -\infty$ and inner products are not used to compute $F$.
  Moreover, since $f$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
	\begin{align*}
	f(p) &= h(p) - \delta(p \mid C)\\
		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
	\end{align*}
\end{proof}

We now extend $f$ from the simplex to the nonnegative reals.
\begin{definition}
	Define the function $g : \reals_+^\Y \to \reals_+$ by extending $-f$
	\begin{align*}
	g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
	\end{align*}
	taking $g(0) = 0$.
\end{definition}
%Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.

@@

\subsection{Projections to the positive orthant}
\begin{itemize}
\item Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
\item 
\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v\in\V^*$ such that $H_v$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
If there was no $v \in \V^*$ such that $x \in F_v$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
\end{proof}

\item 
\begin{corollary}
	$\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
	% \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
\end{corollary}
\item Note: $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}
\end{itemize}

\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L = f$.}
\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\V}$.
\item 
\begin{claim}
	$G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
\end{claim}
\begin{proof}
	\jessie{If $\H$ is redundant, there is still a finite $\H^*$ such that $\H^* \subseteq \H$... right?  weird if $\H$ is infinite.}
\end{proof}
\item 
\begin{claim}
	Argue that $\H_{\V^*} \subseteq \H$, since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\end{claim}
\item 
\begin{corollary}
	Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
\end{corollary}
\item 
\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\end{claim}
\item Let $r$ be a report, and let $\hat v = L(r)$.
\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
\item Argue that $F_{\hat v}$ must be a subset of one of the $\V^*$ facets $F_v$ (as opposed to the vertical ones)
\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
\item Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
\end{itemize}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\begin{proposition}\label{prop:embed-bayes-risks}
  Let discrete loss $\ell$ and minimizable loss $L$ be given.
  Then $L$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % Let discrete loss $\ell:\R\to\reals^Y$ be given.
  % Then $L:\reals^d\to\reals^\Y$ embeds $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L$ embeds a discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{4/2/2021 first part of the proof should be done now.}
  Define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$, so we have some $\Sc\subseteq \R$ which is representative for $\ell$ and an embedding $\varphi:\Sc\to\reals^d$; take $\U := \varphi(\Sc)$.
  Since $\Sc$ is representative for $\ell$, by embedding condition (ii) we have $\{\gamma_s \mid s\in\Sc\} = \{\Gamma_u \mid u\in\U\}$, so $\U$ is representative for $L$.
  % for all $p\in\simplex$ we have some $r \in \Sc \cap \gamma(p)$ and thus we have $\varphi(r) \in \U \cap \Gamma(p)$.
  % In particular, $\U \cap \Gamma(p)\neq \emptyset$ for all $p\in\simplex$, 
  By Lemma~\ref{lem:loss-restrict}, we have $\risk{\ell} = \risk{\ell|_{\Sc}}$ and $\risk{L} = \risk{L|_{\U}}$.
  % \raft{Commented out: the symmetric argument that representation goes both ways under an embedding.  I'm thinking we should expand on this perspective in section 5, maybe introduce a notion of equivalence between any two losses (discrete or otherwise), and define trim in that context.}
  % Taking $\U := \varphi(\Sc)$, we have that $\ell$ if and only if $\U$ is representative of $L$, as $\gamma(p) \cap \Sc \neq \emptyset \iff \exists r \in \Sc$ such that $r \in \gamma(p) \iff \exists r$ such that $\varphi(r) \in \Gamma(p) \cap \U \iff \Gamma(p) \cap \U \neq \emptyset$.
%  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), for all $p\in\simplex$ we have
  \begin{equation*}
    \risk{\ell}(p) = \risk{\ell|_\Sc}(p) = \min_{r \in \Sc}\inprod{p}{\ell(r)} = \min_{r \in \Sc}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~.
  \end{equation*}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell:\R \to \reals^\Y_+$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  \raf{We will apply Theorem (bayes-risk-matching), which we prove in \S~\ref{sec:min-rep-sets}}
  Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\cite[Corollary 13.3.1]{rockafellar1997convex}.
  Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.
  Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
  As $C$ is polyhedral, so is $L$.
  We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.

@@

\section{Additional Structure of Embeddings}
\label{sec:min-rep-sets}

\raf{Start w/ Lemma X}

\subsection{Equivalent condition: matching Bayes risks}

\subsection{Minimum Representative Sets and Non-redundancy}
% commented out 19 Apr 21
% \raf{Some thoughts on this section:
% \begin{itemize}
% \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
% \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
%   \begin{itemize}
%   \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
%   \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
%   \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
%   \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
%   \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
%   \end{itemize}
% \end{itemize}}
% \jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
% There are a few results that are well-explained by this:
% \begin{itemize}
%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimum representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
% \end{itemize}
% This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

@@

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
  Let $\U$ be a finite representative set for $L$.
  $\U$ is a minimum representative set for $L$ if and only if $L|_{\U}$ is non-redundant.
\end{proposition}
\begin{proof}
  Let $L$ elicit $\Gamma$.
  $\Rightarrow$  
  We show the contrapositive: suppose $L|_{\U}$ is redundant.
  Then there is a $r,r' \in \U$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
  Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
  Therefore, $\U \setminus \{r\}$ still a representative set, so $\U$ is not minimum.

@@

\begin{definition}
	Define the function $g : \reals_+^\Y \to \reals_+$ by
	\begin{align*}
	g(x) = \min_{v\in\V} \inprod{x}{v} - \delta(x \mid \reals_+^\Y)~,~
	\end{align*}
	taking $g(0) = 0$.
\end{definition}
%Extend to $g(x) = \min_{v\in\V} \inprod{x}{v}$ for $x \in \reals^\Y_+$ and $g(x) = -\infty$ otherwise.  Def $g(0) = 0$.

@@

\subsection{Projections to the positive orthant}

Define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.

\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v\in\V^*$ such that $H_v$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
We can write any face $F_v = H_v \cap G = \{x \in \reals_+^{d-1} \mid \inprod{x}{v} = g(x)\}$.
If there was no $v \in \V^*$ such that $x \in F_v$, then $g(x) = \min_{H_v \in \H_\Y} \inprod{v}{x}$.
As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
\end{proof}

\begin{corollary}
	$\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
	% \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
\end{corollary}

\subsection{Phase 2: Now given a minimizable loss $L:\R\to\reals^\Y_+$ with $\risk L_+ = g$ (1-homog extension).}

For $x\in\reals^\Y_+$,
$\risk{L}_+(x) := \inf_{r\in\R} \inprod{x}{L(r)}$

\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\V}$.
\begin{claim}
	$G = \cap\H$ by definition of $\risk{L}$ \raf{prove}
\end{claim}
\begin{proof}
  \raf{Let $(x,c) \in G$.  Show $(x,c)\in\cap \H$.  Then vice versa.  Or maybe iff once you get the hang of it.}

  $\implies$
  Have $g(x) \geq c$... use $g=\risk{L}_+$... then for all loss vectors $v = L()$, $(x,c) \in H_v^+$.  Done.

  Other dir: for any $(x,c) \in \cap \H$
	\jessie{If $\H$ is redundant, there is still a finite $\H^*$ such that $\H^* \subseteq \H$... right?  weird if $\H$ is infinite.}
\end{proof}
\item Need to use minimizable
\begin{claim}
	Argue that $\H_{\V^*} \subseteq \H$, since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\end{claim}
\item 
\begin{corollary}
	Conclude there is some set $\R^* \subseteq \R$ such that $L(\R^*) = \V^*$ (without duplicates).
\end{corollary}
\item 
\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$,  $\dim(\pi(F_v)) = \dim(F_v)-1$.
\end{claim}
\item Let $r$ be a report, and let $\hat v = L(r)$.
\item As $H_{\hat v}^+ \in \H$, it supports $G$ or it is redundant in $\H$ (or both).
\item If it does support $G$, then $F_{\hat v} = H_{\hat v}^+ \cap G$ is a face of $G$, and thus a subset of a facet.
\item Argue that $F_{\hat v}$ must be a subset of one of the $\V^*$ facets $F_v$ (as opposed to the vertical ones)
\item Thus, $\pi(F_{\hat v}) \subseteq \pi(F_v)$. \raf{This will show (3) once we translate back}
\item Claim: $\R'$ is a rep set for $L$ if and only if $\V \subseteq L(\R')$.
\item Corollary: $\R^*$ is a min rep set for $L$ if and only if $\V^* = L(\R^*)$. \raf{(1)}
\end{itemize}

\subsection{Translating to properties}

Let $f:\reals^\Y\to\reals_+\cup\{-\infty\}$ be a polyhedral concave function with $\dom(f) = \simplex$.
\begin{claim}
	We may write $f(p) = \min_{v\in\V} \inprod{p}{v}$ for some finite set $\V \subseteq \reals^\Y_+$ \raf{show you can do this using the $h$ and $\delta$ representation from Rockafellar -- argue that because $p\in\simplex$ we can write $\inprod{p}{b_i}-\beta_i = \inprod{p}{b_i-\beta_i\ones}$.}
\end{claim}
\begin{proof}
  We will think of $f$ as defined $f:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(f) = \simplex$.
  \raf{Make formal}
  For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
  If $p \not \in \simplex$, then $f(p) = -\infty$ and inner products are not used to compute $F$.
  Moreover, since $f$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written 
	\begin{align*}
	f(p) &= h(p) - \delta(p \mid C)\\
		 &= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
		 &= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)~.~
	\end{align*}
\end{proof}

Note: $\theta(v) = \pi(F_v) \cap \simplex$. \raf{But haven't def $\theta$ yet}

Argue $\theta(v)$ is full-dim in $\simplex$ if and only if $\pi(F_v)$ is $|\Y|$-dim, if and only if $F_v$ is a facet. \raf{(2)}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
